test

### 2023-05-06 manuscript/paper.Rmd
check,

---
title: |
  |  \Large Optimal K: some titles
author: |
 | \large Mena Whalen 
  \vspace{-1.1mm}
   \normalsize Department of Mathematics and Statistics \vspace{-1mm}
  | \normalsize Loyola University Chicago \vspace{-1mm}
   | \normalsize Chicago, IL 60660 \vspace{-1mm}
   | \normalsize [`mwhalen3@luc.edu`](mailto:mwhalen3@luc.edu) \vspace{-1mm}

   \large Gregory J. Matthews 
  \vspace{-1.1mm}
   \normalsize Department of Mathematics and Statistics \vspace{-1mm}
   \normalsize Loyola University Chicago \vspace{-1mm}
   \normalsize Chicago, IL 60660 \vspace{-1mm}
   \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1mm}

abstract: |
  | Abstract \vspace{2mm}
  | *Keywords*: Cross validation  
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

>>>>

---
title: "test"
author: 
  - "Angelos Vasilopoulos"
  - "Gregory J. Matthews"
abstract: |
  | Abstract \vspace{2mm}
  | *Keywords*: Cross validation  
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---
